---
title: "Untitled"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library( dplyr )
```

## DGP

The model is taken from Chan (2013) Moving Average Stochastic Volatility Models with Application to Inflation Forecast, Journal of Econometrics, 176(2), 162-172.

\begin{align}
y_t &= \mu_t + \varepsilon_t^y \\
\varepsilon_t^y &= u_t + \psi u_{t-1}  & & u_t \sim N(0, \exp^{h_t}) \\
h_t &= \mu_h + \phi_h( h_{t-1} - \mu_h ) + \varepsilon_t^h & & \varepsilon_t^h \sim N(0, \sigma^2_h)
\end{align}

```{r dgp, echo=TRUE}
set.seed( 17 )

nobs = 100
nobs_burn = 100
q = 1

nobs_ = nobs + q + nobs_burn

# parameters of SV equation
sd_h  = 0.1
phi_h = 0.95
mu_h  = 0.1
eps_h = rnorm( nobs_, sd = sd_h)

psi_u = 0.5
mu_y  = 1
phi_y = 0.7

### generate standard deviation of the error for the dependent variable
h_ <- arima.sim(list(order=c(1,0,0), ar=phi_h), n=nobs_, innov = eps_h) %>% c
h  <- h_ + mu_h / ( 1 - phi_h )  

### check generated h:
if(FALSE){ 
    data_h = data.frame( h =h, h_1 = dplyr::lag( h, n = 1 ) ) %>% na.omit
    lm( h ~ h_1, data = data_h ) %>% summary
}

### generate variance of error term in dependent variable
sd_u = exp( h / 2 ) 


u = sapply( sd_u, function( x ) rnorm( 1, mean = 0, sd = x ) )
#u = rnorm( nobs_, mean = 0, sd = mean(sd_u) )

### MA(1) for eps_y
eps_y = arima.sim(list(order=c(0,0,1), ma = psi_u ), n=nobs_, innov = u ) %>% c
arima( eps_y, order = c(0,0,1))


### generate AR(1) model
y_ = arima.sim(list(order=c(1,0,0), ar=phi_y), n=nobs_, innov = eps_y) %>% c
#y_ = arima.sim(list(order=c(1,0,1), ar=phi_y, ma = psi_u), n=nobs_, innov = u) %>% c
y  = y_ + mu_y / ( 1 - phi_y ) 

### discard burin in
y     = y[     -seq( 1 : (q + nobs_burn) ) ]
sd_u  = sd_u[  -seq( 1 : (q + nobs_burn) ) ]
eps_y = eps_y[ -seq( 1 : (q + nobs_burn) ) ]

plot( sd_u , type = "l", main = "sd_u" )  
plot( u    , type = "l", main = "u" ); abline( v = q + nobs_burn, col = "red", lwd = 2 )
plot( eps_y, type = "l", main = "eps_y" )
plot(     y, type = "l", main = "y" )

### estmate AR(1)-MA(1)
arima( y, order = c(1,0,1))
summary( sd_u )

```
## AR(1)-MA model
Translated from MATLAB code AR1MA.m
```{r prior}


q = 2 ; ### # of AR lags + intercept

phih0 = .9; invVphih = 1;
muh0 = 0; invVmuh = 1/5;
nuh = 10; Sh = .05*(nuh-1);
invVbeta = rep(1, q)/5; # ones(q,1)/5;
invVpsi = 1;

# # initialize the Markov chain
# X = [ones(T,1) [y0(end); y(1:end-1)] ];
# psi = 0;
# beta = (X'*X)\(X'*y);
# muh = 0; phih = .8; sigh2 = .1;
# h = log(var(y-X*beta))*ones(T,1);
# psihat = psi;
# invDpsic = .01;
# countpsi = 0;
# countphih=0;
# 
# % initialize for storage
# stheta = zeros(nloop-burnin,3);
# sbeta = zeros(nloop-burnin,q);
# spsi = zeros(nloop-burnin,1);
# sh = zeros(nloop - burnin,T);
# 
# %% construct a few things
# newnuh = T/2 + nuh;
# psipri = @(x) -log(normpdf(x,0,sqrt(1/invVpsi))/(normcdf(sqrt(invVpsi))-normcdf(-sqrt(invVpsi))));
# Hpsi = speye(T) + sparse(2:T,1:(T-1),psi*ones(1,T-1),T,T); 
# 
# disp('Starting AR(1)-MA.... ');
# disp(' ' );
# start_time = clock;    
# 
# rand('state', sum(100*clock) ); randn('state', sum(200*clock) );


```

## Including Plots

You can also embed plots, for example:

```{r pressure00, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
